Illustrating Good Practice in {\LaTeX}

### 2022-03-27 article/article.tex
renamed directory
fixed whitespace problem

\title{Illustrating Good Practice in {\LaTeX}}
\author{Nicholas D. Kostin}
\date{March 2022}

@@

\begin{mdframed}[backgroundcolor=black!4, align=center, userdefinedwidth=40em, topline=false, bottomline = false, leftline = false, rightline = false, frametitle = {Bolzano-Weierstrass Theorem}]
Every bounded sequence has a convergent subsequence.
\end{mdframed}

@@

\begin{mdframed}[backgroundcolor=black!4, align=center, userdefinedwidth=40em, topline=false, bottomline = false, leftline = false, rightline = false, frametitle = {Lemma}]
Cauchy sequences are bounded.
\end{mdframed}

>>>>

\title{Illustrating Good Practice in {\LaTeX}}
\author{Nicholas D. Kostin}
\date{May 2022}

@@

\begin{mdframed}[backgroundcolor=black!4, align=center, userdefinedwidth=40em, topline=false, bottomline=false, leftline=false, rightline=false, frametitle={Bolzano-Weierstrass Theorem}]
Every bounded sequence has a convergent subsequence.
\end{mdframed}

@@

\begin{mdframed}[backgroundcolor=black!4, align=center, userdefinedwidth=40em, topline=false, bottomline=false, leftline=false, rightline=false, frametitle={Lemma}]
Cauchy sequences are bounded.
\end{mdframed}
